On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-13 2_bg.tex
Minor

>>>>

\textcolor{red}{
This paper is based on a preliminary version published at 
SIGIR 2015~\cite{ME-SIGIR15}, but adds: RQ2; 
related background on crowdsourcing;
more information on the score distributions in Section~\ref{sec:descr-stat}, including
Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores} and their discussion;
a new Section~\ref{sec:cs} including Figure~\ref{fig:judgeVariability} and 
recomputation of Figure~\ref{fig:workersQuality};
new material in Section~\ref{sec:rq2}, including recomputation of 
Figures~\ref{fig:runs-rerank-median3best} and~\ref{fig:runs-rerank-median3best-fake}; 
a revised second half of Section~\ref{sec-rq3}; 
an Appendix giving exact participant instructions; and
additional references.
}
